ShabbyPages: A Reproducible Document Denoising and Binarization Dataset

### 2023-02-11 paper/paper.tex

Other prior work includes several datasets for the related task of document image binarization, which seeks to convert a document image into a binary image, where foreground text is black and background pixels are white.
Among the most important in this class are the \emph{DIBCO} collections \cite{dibco-09,dibco-10,dibco-11,dibco-12,dibco-13,dibco-14,dibco-16,dibco-17,dibco-18}.
As summarized in Table~\ref{tab:datasets}, the \emph{DIBCO} family of datasets is very small, ranging between 10 and 20 samples each (for a total of 106 images across \emph{DIBCO-9} through \emph{DIBCO-18}).
Similar to \emph{NoisyOffice}, the \emph{DIBCO} datasets do not contain graphical elements like images, tables, charts, etc.
The Persian Heritage Image Binarization Dataset (PHIBD) \cite{phibc-2012-nafchi,nafchi-2013-icdar} is similar to the \emph{DIBCO} benchmarks, consisting of a small number of images of handwritten Persian writing.
Others, like the Bickley Diary set \cite{bickley-diary} and the 2019 Time-Quality Binarization Competition set \cite{2019-time-quality-competition} have also been used for benchmarking document binarization approaches, but these do not appear to be publicly available \cite{tensmeyer-binarization-review-2020}.
Ultimately, the sizes of these document binarization corpora severly limit the types of algorithms and models that can be used.
Examples of noisy-clean image pairs from some of these collections are displayed in Figure~\ref{fig:other-dataset-examples}.

@@

Other popular document image datasets --- like RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 [CITE], Tobacco-800 \cite{ref_Tobacco800}, and FUNSD [cite] --- include large amounts of real noise, but none of these have corresponding clean ground-truth document images to train or evaluate document denoisiers and binarizers.

>>>>

Other prior work includes several datasets for the related task of document image binarization, which seeks to convert a document image into a binary image, where foreground text is black and background pixels are white.
Among the most important in this class are the \emph{DIBCO} collections \cite{dibco-09,dibco-10,dibco-11,dibco-12,dibco-13,dibco-14,dibco-16,dibco-17,dibco-18}.
As summarized in Table~\ref{tab:datasets}, the \emph{DIBCO} family of datasets is very small, ranging between 10 and 20 samples each (for a total of 106 images across \emph{DIBCO-9} through \emph{DIBCO-18}).
Similar to \emph{NoisyOffice}, the \emph{DIBCO} datasets do not contain graphical elements like images, tables, charts, etc.
The Persian Heritage Image Binarization Dataset (PHIBD) \cite{phibc-2012-nafchi,nafchi-2013-icdar} is similar to the \emph{DIBCO} benchmarks, consisting of a small number of images of handwritten Persian writing.
Others, like the Bickley Diary set \cite{bickley-diary} and the 2019 Time-Quality Binarization Competition set \cite{2019-time-quality-competition} have also been used for benchmarking document binarization approaches, but these do not appear to be publicly available \cite{tensmeyer-binarization-review-2020}.
Ultimately, the sizes of these document binarization corpora severely limit the types of algorithms and models that can be used.
Examples of noisy-clean image pairs from some of these collections are displayed in Figure~\ref{fig:other-dataset-examples}.

@@

Other popular document image datasets --- like RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 [CITE], Tobacco-800 \cite{ref_Tobacco800}, and FUNSD [cite] --- include large amounts of real noise, but none of these have corresponding clean ground-truth document images to train or evaluate document denoisers and binarizers.
